SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-05 docs/questioning.tex
some changes / additions

In this paper we initially show how the above attacks can be seen from
a {\it common perspective}. We achieve this by providing an
exploitation model that highlights the following fact: the majority of
the steps needed to perform application attacks based on executable
source code injection are common.\footnote{Note that we leave out
  attacks that are based on binary code injection (i.e. buffer
  overflows --- see Section~\ref{sec:attacks}).} This is validated by
the fact that there are protection mechanisms that can detect more
than one of these attacks. Then, we {\it categorize} a selection of
these protection mechanisms. The selection comprises protection
mechanisms that detect such attacks and are presented in publications
cited more than twenty times, and some of the latest mechanisms that
have been presented in top security conferences that have been cited
less than twenty times. We included the second group so that we would
not penalize recent research. Finally, we {\it analyze} each mechanism based
on the following dimensions:
\begin{itemize}
\item {\it Diagnostic Performance} Protection mechanisms are as good
  as their detection capability; this requires low false positive and
  false negative rates.
\item {\it Computational Performance} We examine
the overhead of the mechanisms
that affect the experience of a web user who actually
uses the protected application.
\item {\it Ease of use} We examine if the protection
mechanism is practical in terms of deployment
and can be easily adopted by security experts.
\item {\it Security} How resilient is the system to
attackers that know how it works and wants to circumvent it.
\item {\it Detection Locus}
\item {\it Availability}
\end{itemize}

\noindent
All the aforementioned requirements are considered critical
when building security mechanisms that protect
applications~\cite{A01,A00}. Based on this analysis
we can identify the advantages and disadvantages of the
various mechanisms and enumerate some of their common
characteristics. We can also draw useful conclusions
about the various categories and see how they compare
to each other.

@@

In this section we provide a step-by-step exploitation model to
understand the process of carrying out application attacks based on
executable source code injection vulnerabilities.
Figure~\ref{fig:attacks} presents the steps of different application
attacks. For every arrow there is a
corresponding tuple that includes the step number for
every attack. For the most part, the steps are common in all attacks. This
is because they are based on similar attack vectors as we mentioned in
the previous section. Most importantly,
Figure~\ref{fig:attacks} also illustrates in which step
the defenses detect corresponding attacks ({\sc todo}).

@@

    \item[3] The number involve requests.

@@

\begin{figure}
\begin{center}
\leavevmode
\includegraphics[scale=0.47]{defect-percentages.png}
\end{center}
\caption{\label{fig:defect_sources}A pie showing where the
authors reffered to, to find vulnerabilities to test
their mechanims. We also provide which source was used
by which publication:
{\it Bugtraq}~\cite{PB05,KKVJ06,KJKV09,JEP08},
{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09,JKK06a},
{\sc xss}ed.com~\cite{NSS06,APKLM10},
ha.ckers.org~\cite{TNH07,PSC09,LV09},
Microsoft~\cite{RDWDE07}.}
\end{figure}

>>>>

In this paper we initially show how the above attacks can be seen from
a {\it common perspective}. We achieve this by providing an
exploitation model that highlights the following fact: the majority of
the steps needed to perform application attacks based on executable
source code injection are common.\footnote{Note that we leave out
  attacks that are based on binary code injection (i.e. buffer
  overflows --- see Section~\ref{sec:attacks}).} This is validated by
the fact that there are protection mechanisms that can detect more
than one of these attacks. Then, we {\it categorize} a selection of
these protection mechanisms. The selection comprises protection
mechanisms that detect such attacks and are presented in publications
cited more than twenty times, and some of the latest mechanisms that
have been presented in top security conferences that have been cited
less than twenty times. We included the second group so that we would
not penalize recent research. Finally, we {\it analyze} each mechanism based
on the following dimensions:
\begin{itemize}
\item {\it Diagnostic Performance} Protection mechanisms are as good
  as their detection capability; this requires low false positive and
  false negative rates.
\item {\it Computational Performance} We examine
  the overhead of the mechanisms
  that affect the experience of a web user who actually
  uses the protected application.
\item {\it Ease of use} We examine if the protection
  mechanism is practical in terms of deployment
  and can be easily adopted by security experts.
\item {\it Security} We examine how resilient is the system to
  attackers that know how it works and wants to circumvent it.
\item {\it Detection Locus} Based on our exploitation model
  we examine the location where a mechanism detects an attack.
\item {\it Availability} We check if the mechanism and its
  testbed are available on-line.
available 
\end{itemize}

\noindent
All the aforementioned requirements are considered critical
when building security mechanisms that protect
applications~\cite{A01,A00,SPWS13}. Based on this analysis
we can identify the advantages and disadvantages of the
various mechanisms and enumerate some of their common
characteristics. We can also draw useful conclusions
about the various categories and see how they compare
to each other.

@@

In this section we provide a step-by-step exploitation model to
understand the process of carrying out application attacks based on
executable source code injection vulnerabilities.
Figure~\ref{fig:attacks} presents the steps of different application
attacks. For every arrow there is a
corresponding tuple that includes the step number for
every attack. For the most part, the steps are common in all attacks. This
is because they are based on similar attack vectors as we mentioned in
the previous section. Most importantly,
Figure~\ref{fig:attacks} also illustrates in which step
the defenses detect corresponding attacks.

@@

    \item[3] The numbers of this quadruple involve requests.

@@

\begin{figure}
\begin{center}
\leavevmode
\includegraphics[scale=0.47]{defect-percentages.png}
\end{center}
\caption{\label{fig:defect_sources}A pie showing the sources
where the authors reffered to, to find vulnerabilities to test
their mechanisms. We also provide which source was used
in which publication:
{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09,JKK06a},
{\it Bugtraq}~\cite{PB05,KKVJ06,KJKV09,JEP08},
{\sc xss}ed.com~\cite{NSS06,APKLM10},
ha.ckers.org~\cite{TNH07,PSC09,LV09},
Microsoft~\cite{RDWDE07}.}
\end{figure}
